\LARGE \bf When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting

### 2014-12-27 main.tex
De-anonymized + copyright for final submission

%
% --- Author Metadata here ---
\conferenceinfo{10th ACM/IEEE International Conference on Human-Robot Interaction}{2015 Portland, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{1} 
%\author{
%\alignauthor
%Deanna Hood, Séverin Lemaignan, Pierre Dillenbourg\\
%   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
%   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
%   %\affaddr{CH-1015 Lausanne, Switzerland}\\
%   \email{firstname.lastname@epfl.ch}
%}

%(DH) my EPFL email address won't work for much longer....

@@

Robots have been used as teachers or social partners to promote children's
learning in a range of contexts, most commonly related to language
skills~\cite{Han2010}, and less often to physical skills (such as
calligraphy~\cite{Matsui2013}).  Looking at the converse (humans \emph{teaching}
robots), Werfel notes in~\cite{Werfel2014} that most of the work focuses on the
robot's benefits (in terms of language~\cite{Saunders2010} or
physical~\cite{Mulling2013} skills, for example) rather than the learning
experienced by the human tutor themselves.  Our work concentrates on this latter
aspect: by demonstrating handwriting to a robot, we aim at improving the
\emph{child's} performance. Note that our work must be distinguished from
``learning from demonstration'' approaches to robots learning physical skills,
as the agent we present is only simulating fine motor skills for interaction
purposes.

@@

   \label{fig:naoWriting}
\end{figure}
%\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
\footnotetext{See \url{[anonymized]} for a video of the synchronised 
writing demonstration. }

@@

The source code for the teachable robotic handwriting partner has been made 
%available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
available at \url{[anonymized]}.

@@

\begin{figure}[thpb!]
     \begin{center}
%
        \subfigure[The user shows a card to the robot with a word to write.]{%
            \label{fig:first}
            \includegraphics[width=0.2\textwidth]{figures/1anon.jpg}
        }~
        \subfigure[The robot writes the word seen on the card and asks for feedback.]{%
           \label{fig:second}
           \includegraphics[width=0.2\textwidth]{figures/2anon.jpg}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[The user provides feedback on the letters written via demonstration.]{%
            \label{fig:third}
            \includegraphics[width=0.2\textwidth]{figures/3anon.jpg}
        }~
        \subfigure[The robot responds to the feedback, until the user is satisfied.]{%
            \label{fig:fourth}
            \includegraphics[width=0.2\textwidth]{figures/4anon.jpg}
        }%
%
    \end{center}
    \caption{%
        A user engaging with the robot in the \emph{learning by teaching}
    interaction, using demonstrations as feedback.}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Anonymized for double-blind review
%\section*{Acknowledgments}
%
%This research was supported by the Swiss National Science Foundation through the
%National Centre of Competence in Research Robotics.

>>>>

% --- Author Metadata here ---
\conferenceinfo{HRI '15, March 02 - 05 2015,}{Portland, OR, USA}
\CopyrightYear{is held by the owner/author(s). Publication rights licensed to ACM.} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
\crdata{978-1-4503-2883-8/15/03}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{1} 
\author{
\alignauthor
Deanna Hood, Séverin Lemaignan, Pierre Dillenbourg\\
   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
   \affaddr{École Polytechnique Fédérale de Lausanne (EPFL)}\\
   %\affaddr{CH-1015 Lausanne, Switzerland}\\
   \email{firstname.lastname@epfl.ch}
}

@@

Robots have been used as teachers or social partners to promote children's
learning in a range of contexts, most commonly related to language
skills~\cite{han2010robot}, and less often to physical skills (such as
calligraphy~\cite{Matsui2013}).  Looking at the converse (humans \emph{teaching}
robots), Werfel notes in~\cite{Werfel2014} that most of the work focuses on the
robot's benefits (in terms of language~\cite{Saunders2010} or
physical~\cite{Mulling2013} skills, for example) rather than the learning
experienced by the human tutor themselves.  Our work concentrates on this latter
aspect: by demonstrating handwriting to a robot, we aim at improving the
\emph{child's} performance. Note that our work must be distinguished from
``learning from demonstration'' approaches to robots learning physical skills,
as the agent we present is only simulating fine motor skills for interaction
purposes.

@@

   \label{fig:naoWriting}
\end{figure}
\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video
of the synchronised writing demonstration. }

@@

The source code for the teachable robotic handwriting partner has been made 
available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.

@@

\begin{figure}[thpb!]
     \begin{center}
%
        \subfigure[The user shows a card to the robot with a word to write.]{%
            \label{fig:first}
            \includegraphics[width=0.2\textwidth]{figures/1card}
        }~
        \subfigure[The robot writes the word seen on the card and asks for feedback.]{%
           \label{fig:second}
           \includegraphics[width=0.2\textwidth]{figures/2word}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[The user provides feedback on the letters written via demonstration.]{%
            \label{fig:third}
            \includegraphics[width=0.2\textwidth]{figures/3ask}
        }~
        \subfigure[The robot responds to the feedback, until the user is satisfied.]{%
            \label{fig:fourth}
            \includegraphics[width=0.2\textwidth]{figures/4correct}
        }%
%
    \end{center}
    \caption{%
        A user engaging with the robot in the \emph{learning by teaching}
    interaction, using demonstrations as feedback.}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Anonymized for double-blind review
\section*{Acknowledgments}

This research was supported by the Swiss National Science Foundation through the
National Centre of Competence in Research Robotics.
